# Multifractal analysis of multispecies spatial distributions - Model simulations 

I generate parameter files for the simulation of neutral/hierarchical model using logseries as the metacommunity distribution


```{r setup, eval=T }

simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"


require(pander)
panderOptions('table.split.table',Inf)

```

This is run only once to generate the metacommunity then set eval=FALSE and generate
a set of parameter files to modify 


```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

require(untb)
side <- 500
N <- side*side
S <- 450 
ff<-fisher.ecosystem(N=N,S=S,nmax=N)
plot(ff)
nrow(ff)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

spMeta <- nrow(ff)

# Parameters
#
# Mortality = 0.2 - 0.4
# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
#                         2.5 -> 0.4
# Colonization = 0.001 -0.0001
# Replacement  = 0 - 1

setwd("Simul")
#undebug(genNeutralParms)
# First generate de inp file with species and metacommunity parameters 
genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)

# Then pomac.lin to simulate a range of parmeters and repetitions.
#
# Generates pomac.lin for multiple simulations exponential dispersal to compare hierarchical and neutral communities  
# and see when they have similar H and compare if they have similar SAD

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))

# we need the par file with the simulations parameters


par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 10
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters 


write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)


# Run the model with the parameter ReplacementRate turned on = Hierarchical 
# and exponential dispersal 
#
# Set the location of the binary 
#neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)


```

## Simulations with different parameters using pomac and at Time=100

Now I will simulate the model to Time=100 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and ten repetitions 


```{r simul_pomac467_T100, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

spMeta <- 467 # nrow(ff) number of species in the generated metacommunity 

bName <- paste0("Exp", spMeta) # Base name based in the dispersal "Exp" and number of species in metacommunity "467"



if(simul) {

  # Delete old simulations
  system("rm Exp467T100*")

  # read par file with simulations parameters

  par <- read.table("sim.par",quote="",stringsAsFactors=F)

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 100

  par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0(bName ,"T100") # Time = 100 
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters 

  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

  # I have to modify pomExp.lin to make different simulations
  #undebug(genPomacParms)

  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)

  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")

  system(paste(neuBin,"sim.par","fishE.inp"))
}

m <- compMethods_Time(bName,100,spMeta) 

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SAD",]

# Which are not different
#pander(mks1[mks1$p.adjust>0.05,],caption="SAD not different")

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
# Select a subset to test the procedure !
#
#den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]

require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

# Plot the first pairs not different 
#

mks <- mks1[mks1$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line() + ggtitle("SAD not dif"))


# Plot the first pair different 
#
mks <- mks1[mks1$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line()
 + ggtitle("SAD different"))


# Calculate ranks for each parameter combination with different ReplacementRate
#
den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
den3 <- calcRankSAD(den2)

(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())


rm(mks,psa,den2)

#
# Now check differences using multifractals mfSAD o mfSRS
#

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))

# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
#

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001, "SRS")
plotDq_ReplaceR(Dq1,0.2,0.4,0.001, "SRS")
plotDq_ReplaceR(Dq1,0.2,0.04,0.001, "SRS")

#mks1 <- m$mPval
#mks1 <- mks1[mks1$method=="SRS" & mks1$p.adjust>0.05,]
#pander(mks1,split.tables=Inf,caption="SRS not different")

# NO FUNCIONA MERGE
#psa <- mergePairSAD(mks[1,],Dq1)

#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))

plotDq_ReplaceR(Dq1,0.2,0.04,0.001,"DqSAD")
plotDq_ReplaceR(Dq1,0.2,0.4,0.001,"DqSAD")
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001,"DqSAD")


mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
#pander(mks1,caption="DqSAD not different")


# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!

compM <- m$compM

mPval <- m$mPval


setwd(oldcd)
rm(Dq1,den1)
rm(den1,den,mks1,mks,mks100)
save.image()

```

## Simulations at Time=500


```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }
load(".RData")

setwd("Simul")

# read par file with simulations parameters
if(simul)
{
  # Delete old simulations
  system("rm Exp467T500*")
    
  par <- read.table("sim.par",quote="",stringsAsFactors=F)
  
  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 500
  par[par$V1=="inter",]$V2 <- 500 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 500  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T500")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters 
  
  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
  
  # I will not delete old simulations
  # system("rm Exp467*")
  
  # I have to modify pomExp.lin to make different simulations
  
  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)
  
  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")
  
  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  system(s,wait=F)
}

m <- compMethods_Time(bName,500,spMeta) 


compM <- rbind(compM,m$compM)

pander(compM,caption="Proportion of not different")


mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T=500")

Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))

mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different T=500")

mPval <- rbind(mPval,m$mPval)

mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]


setwd(oldcd)
rm(Dq1,m,mks1)
save.image()

```

Now the same set of simulations for T=1000

```{r simul_pomac467_T1000, eval=T,echo=F,message=F,warning=F}

# Load data if run only one chunk 
#load(".RData")

setwd("Simul")

if(simul)
{
  # Delete old simulations
  system("rm Exp467T1000*")
    
  # read par file with simulations parameters

  par <- read.table("sim.par",quote="",stringsAsFactors=F)

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 1000
  par[par$V1=="inter",]$V2 <- 1000 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 1000  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T1000")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters 

  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

  # I have to modify pomExp.lin to make different simulations

  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)

  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")

  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  if(simul) system(s,wait=F)
}

m <- compMethods_Time(bName,1000,spMeta) 

compM <- rbind(compM,m$compM)

pander(compM,caption="Proportion of not different")


mks1 <- m$mPval
mks1 <- mks1[mks1$method=="DqSAD" & mks1$p.adjust>0.05,]
pander(mks1,caption="DqSAD not different T1000")

mPval <- rbind(mPval,m$mPval)

setwd(oldcd)
rm(m,mks1)
save.image()


``` 

The the proportion of different SAD is constant from T=500 it seems we reach steady state. I have to compare now using H and Dq, for that I should do repeated simulations
of each combination.

```{r plot_Time_pomac467,eval=T,echo=F,message=F,warning=F}

setwd("Simul")

# Plot different SAD with time

# Plot different Dq SRS with time

Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfOrd.txt")))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfOrd.txt")))

mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust>0.05,]

mergePair_plotDq(mks1[1,],Dq1,"SRS not different")

mks1 <- mPval[mPval$method=="SRS" & mPval$p.adjust<=0.05,]

mergePair_plotDq(mks1[4,],Dq1,"SRS different")


# Plot different Dq SAD with time


Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T500mfSAD.txt")))
Dq1 <- rbind(Dq1,readNeutral_calcDq(paste0(bName,"T1000mfSAD.txt")))

mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust>0.05,]

mergePair_plotDq(mks1[1,],Dq1,"DqSAD not different")

mks1 <- mPval[mPval$method=="DqSAD" & mPval$p.adjust<=0.05,]

mergePair_plotDq(mks1[4,],Dq1,"DqSAD different")



setwd(oldcd)

```

```{r compKS_pomac467,eval=T,echo=F,message=F,warning=F}
source("R/Neutral_fun.r")

setwd("Simul")

m <- compMethod_DqKS_Time(bName,100,spMeta) 

compM <- rbind(compM,m$compM)

pander(compM,caption="Proportion of not different")

mPval <- rbind(mPval,m$mPval)


m <- compMethod_DqKS_Time(bName,500,spMeta) 
compM <- rbind(compM,m$compM)
pander(compM,caption="Proportion of not different")
mPval <- rbind(mPval,m$mPval)


m <- compMethod_DqKS_Time(bName,1000,spMeta) 
compM <- rbind(compM,m$compM)
pander(compM,caption="Proportion of not different")
mPval <- rbind(mPval,m$mPval)

setwd(oldcd)

rm(m)

compM

save.image()

names(mPval)
unique(mPval$method)
m <- with(mPval,mPval[method=="DqSADKS" & time==100,])
propNotDiffSAD(m)



```

