# Multifractal analysis of multispecies spatial distributions - Model simulations 

I generate parameter files for the simulation of neutral/hierarchical model using logseries as the metacommunity distribution


```{r setup, eval=T }

simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

```

This is run only once to generate the metacommunity then set eval=FALSE and generate
a set of parameter files to modify 


```{r generateLogSerParms, eval=FALSE,echo=F,message=F,warning=F}
# Generate a SAD for metacommunity using a logseries 
#
# side is the side of the simulation lattice
#
# N is the total number of individuals 
#
# S is the species richness 
#

require(untb)
side <- 500
N <- side*side
S <- 450 
ff<-fisher.ecosystem(N=N,S=S,nmax=N)
plot(ff)
nrow(ff)
ff <- data.frame(sp="",FreqT=as.numeric(ff),prob=0,Ord=1:length(ff))
ff$prob <- ff$FreqT/sum(ff$FreqT)

# Parameters
#
# Mortality = 0.2 - 0.4
# Mean Dispersal distance 25  -> Exponential kernel parm  0.04
#                         2.5 -> 0.4
# Colonization = 0.001 -0.0001
# Replacement  = 0 - 1

setwd("Simul")
#undebug(genNeutralParms)
# First generate de inp file with species and metacommunity parameters 
genNeutralParms("fishE",500,ff$prob,1,0.2,0.04,0.001)

# Then pomac.lin to simulate a range of parmeters and repetitions.
#
# Generates pomac.lin for multiple simulations exponential dispersal to compare hierarchical and neutral communities  
# and see when they have similar H and compare if they have similar SAD

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,1))

# we need the par file with the simulations parameters


par <- read.table("sim.par",quote="",stringsAsFactors=F)
# Change base name

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 100
# Change interval to measure Density and Diversity
par[par$V1=="inter",]$V2 <- 10
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "S" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff))
par[par$V1=="pomac",]$V2 <- 0 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters 


write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)


# Run the model with the parameter ReplacementRate turned on = Hierarchical 
# and exponential dispersal 
#
# Set the location of the binary 
#neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralExp"

# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)


```

## Simulations with different parameters using pomac and at Time=100

Now I will simulate the model to Time=100 with a full set of parameters 
Replacement = 0,0.001,0.01,0.1,1 and ten repetitions 


```{r simul_pomac467_T100,echo=F,message=F,warning=F}

setwd("Simul")

spMeta <- 467 # nrow(ff) number of species in the generated metacommunity 

bName <- paste0("Exp", spMeta) # Base name based in the dispersal "Exp" and number of species in metacommunity "467"



if(simul) {

  # Delete old simulations
  system("rm Exp467T100*")

  # read par file with simulations parameters

  par <- read.table("sim.par",quote="",stringsAsFactors=F)

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 100

  par[par$V1=="inter",]$V2 <- 100 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 100  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0(bName ,"T100") # Time = 100 
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters 

  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

  # I have to modify pomExp.lin to make different simulations
  #undebug(genPomacParms)

  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.001,0.01,0.1,1),10)

  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")


  system(paste(neuBin,"sim.par","fishE.inp"))
}

# Read all simulations and change to long format

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)

# have to make averages of 
require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

names(den2)[6] <- "value" # the functions use this field name

# Select a subset to test the procedure !
#
#den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]

mks100 <- pairKS_SAD(den2)

# Which are not different
format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
compM <- data.frame(time=100,notdif=propNotDiffSAD(mks100),method="SAD")  


# Plot the first pairs not different 
#
mks <- mks100[mks100$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())



# Plot the first pair different 
#
mks <- mks100[mks100$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())


# Calculate ranks for each parameter combination with different ReplacementRate
#
den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
den3 <- calcRankSAD(den2)

(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())


rm(mks,psa,den1,den2,den3)

#
# Now check differences using multifractals mfSAD o mfSRS
#

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfOrd.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="SRS"))

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

c3 <- c2
c3$method <- "SRS"


# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
#

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

# Build data.frame with proportion
#
compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="DqSAD"))



c2$method <- "DqSAD"
c3 <- rbind(c3,c2)                    

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)

# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!

kable(compM)

setwd(oldcd)
rm(c1,c2,Dq2)
rm(den1,den)
save.image()
```

# Simulations at T=500

```{r simul_pomac467_T500, eval=FALSE,echo=F,message=F,warning=F }

setwd("Simul")

# read par file with simulations parameters
if(simul)
{
  system("rm Exp467T100*")
    
  par <- read.table("sim.par",quote="",stringsAsFactors=F)
  
  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 500
  par[par$V1=="inter",]$V2 <- 500 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 500  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T500")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters 
  
  write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)
  
  # I will not delete old simulations
  # system("rm Exp467*")
  
  # I have to modify pomExp.lin to make different simulations
  
  genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))
  
  # copy pomExp.lin to pomac.lin
  system("cp pomExp.lin pomac.lin")
  
  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  system(s)
}

# Read all simulations and change to long format

den1 <- meltDensityOut_NT(paste0(bName,"T500Density.txt"),spMeta)

# have to make averages of 
require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

names(den2)[6] <- "value" # the functions use this field name

# Test pairwise diferences in SAD
#
mks100 <- pairKS_SAD(den2)

# Which are not different
format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSAD(mks100),method="SAD"))  


# Plot the first pairs not different 
#
mks <- mks100[mks100$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())



# Plot the first pair different 
#
mks <- mks100[mks100$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())


# Calculate ranks for each parameter combination with different ReplacementRate
#
den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]
den3 <- calcRankSAD(den2)

(g <- ggplot(den3,aes(x=Rank,y=log(value),colour=parms)) + geom_line())


rm(mks,psa,den1,den2,den3)

#
# Now check differences using multifractals mfSAD o mfSRS
#

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfOrd.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="SRS"))

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

c2$method <- "SRS"
c3 <- rbind(c3,c2)                    


# Plot Dq with differente replacementRate!!!!!!!!!!!!!!!!!!!!!!!!!!
#

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

# Build data.frame with proportion
#
compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="DqSAD"))


c2$method <- "DqSAD"
c3 <- rbind(c3,c2)                    

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)

# Revisar R2 y validez de rangos porque para q positivos da creciente!!!!

kable(compM)

setwd(oldcd)
rm(c1,c2,Dq2)
rm(den1,den)
save.image()

```

Now the same set of simulations for T=1000

```{r simul_pomac467_T1000, eval=FALSE,echo=F,message=F,warning=F}
setwd("Simul")

# read par file with simulations parameters

par <- read.table("sim.par",quote="",stringsAsFactors=F)

# Number of time steps 
par[par$V1=="nEvals",]$V2 <- 1000
par[par$V1=="inter",]$V2 <- 1000 # interval to measure Density and Diversity
par[par$V1=="init",]$V2 <- 1000  # Firs time of measurement = interval
par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T1000")
par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                              # 1:several simulations with pomac.lin parameters 

write.table(par, "sim.par",sep="\t",row.names=F,col.names=F,quote=F)

# I will not delete old simulations
# system("rm Exp467*")

# I have to modify pomExp.lin to make different simulations

genPomacParms("pomExp",1,c(0.2,0.4),c(0.04,0.4),c(0.001,0.0001),c(0,0.01,0.1,1))

# copy pomExp.lin to pomac.lin
system("cp pomExp.lin pomac.lin")

s <- paste(neuBin,"sim.par","fishE.inp")
s
if(simul) system(s,wait=s_wait)

den1 <- meltDensityOut_NT("Exp467T1000Density.txt",nrow(ff))

mks1000 <- pairKS_SAD(den1)

# Which are not different
format(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
nrow(mks1000[mks1000$p.adjust>0.05,c(10:13,14:15)])/nrow(mks1000)


propNotDiffSAD(mks100)  
propNotDiffSAD(mks500)  
propNotDiffSAD(mks1000)  
``` 

The the proportion of different SAD is constant from T=500 it seems we reach steady state. I have to compare now using H and Dq, for that I should do repeated simulations
of each combination.

```{r boot_H_pomac467_T500,eval=FALSE,echo=F,message=F,warning=F}

setwd("Simul")

require(plyr)
require(boot)
require(vegan)

# den <- readWideDensityOut("Exp467T100Density.txt")
num_sp <- nrow(ff)
# how to apply a function to each row of a data frame
hh <- function(x) diversity(x[7:(6+num_sp)])
H <- apply(den,1,hh)

#H <- lapply(den,function(x) diversity(x[7:(6+num_sp)]))
#ldply(H)
# data.frame(colembolos = rowSums(spe[,1:5]), acaros=rowSums(spe[,6:33]),lombrices=rowSums(spe[,34:41]))
den[c(1,7),c("H","Richness")]
den[c(2,4),c("H","Richness")]

difh <- den[c(2,4),7:(6+num_sp)]*(500*500)
difh <- H_bss(difh)

print(difh)
summary(difh)

ciH <-ddply(s_col,.(Ambiente),function(df) boot_shannon(df[,1:5]) )


```

