# Multifractal analysis of multispecies spatial distributions - Simple spatial patterns simulations

I use mfSBA for multifractal estimation: <https://github.com/lsaravia/mfsba>

I generate different a spatial patterns to compare SRSDq SADdq and SAD

```{r setup, eval=T }
load(".RData")

simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA

require(pander)
panderOptions('table.split.table',Inf)
options("scipen"=100, "digits"=4)

```

# Banded pattern of species with uniform  SAD 256 side

First generate a pattern with  SAR z=1 using simply bands of species z=0.5 because I am using area as Borda-de-Agua instead of side.


```{r simul_z1, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- compMethods_UniformSAD(8,256)$Dq

DqF <- rbind(DqF,compMethods_UniformSAD(64,256)$Dq)

DqF <- rbind(DqF,compMethods_UniformSAD(256,256)$Dq)

# Analizing this last it means that the scaling is broken at side 16
#  
#Dq2<- calcDq_multiSBA(fname1,"q.sed 16 1024 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD16-512"
#Dq3<- rbind(Dq3,Dq2)
#
##Dq2<- calcDq_multiSBA(fname1,"q.sed 2 16 20 E",mfBin,T)
#Dq2$Type <- "rnzDqSAD2-16"
#Dq3<- rbind(Dq3,Dq2)
#plotDq(Dq3,"Type")
#require(pander)
#pandoc.table(DqF[DqF$R.Dq<0.8,],caption="R2<0.8")

simul <- 9
require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

ps <- expand.grid(nsp=c(8,64,256),side=c(256),simul=1:9)

cc <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
  compMethods_UniformSAD(ps$nsp[i],256,F)
}

for(i in 1:nrow(ps)) {
  DqF <- rbind(DqF, cc[[i]]$Dq)
  }

setwd(oldcd)
```

* For SRS the positive part seems to reflect the equal SAD and the negative the spatial pattern


# Banded pattern uniform SAD 8,64,256 species 512 side

To see if there is any efect of side 

```{r simul_z1_512, eval=F,echo=F,message=F,warning=F}
setwd("Simul")


DqF <- rbind(DqF,compMethods_UniformSAD(8,512))

DqF <- rbind(DqF,compMethods_UniformSAD(64,512))

DqF <- rbind(DqF,compMethods_UniformSAD(256,512))

setwd(oldcd)
```

Thus DqSAD works in the range 2-8 2-16 2-32 depending on the number of species

For different number of species and different sides the same cualitative patterns are observed.


# Now simulate 10 times simple spatial pattern with logseries SAD with 8, 64 & 256 species,side = 256 

```{r simul_ls_256, eval=F,echo=F,message=F,warning=F}
setwd("Simul")


require(doParallel)
cn <-detectCores()
cl <- makeCluster(cn)
registerDoParallel(cl)
require(foreach)

ps <- expand.grid(nsp=c(8,64,256),side=c(256),simul=1:10)

cc <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
  compMethods_FisherSAD(ps$nsp[i],256,F)
}

for(i in 1:nrow(ps)) {
  DqF <- rbind(DqF, cc[[i]]$Dq)
  }

setwd(oldcd)
save.image()

```

# Test logseries SAD side=512 

```{r simul_ls_512b, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

DqF <- rbind(DqF,compMethods_FisherSAD(8,512))

DqF <- rbind(DqF,compMethods_FisherSAD(64,512))

DqF <- rbind(DqF,compMethods_FisherSAD(256,512))

setwd(oldcd)
save.image()

```

## Plots for publication uniform/Logseries SAD 

```{r plots_spDq, eval=F,echo=F,message=F,warning=F}
setwd("Simul")

# Plot of the Regular and Randomized spatial pattern for a uniform & Logseries SAD with 64 species and side=256
#
g <- plotSAD_SpatPat(64,256,"B")

setwd("..")
ggsave("spat_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
setwd("Simul")


#
# Plots of Dq with uniform/Logseries SAD and 10 repetitions!
#
setwd("..")

g <- plotDq_Side_Sp(DqT,256,0,"B")
g
ggsave("Dq_UniLog_NumSp_256.png", width=8,height=8,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,512,0,"B")
g
ggsave("Dq_UniLog_NumSp_512.png", width=8,height=8,units="in",dpi=600)


#
# Plot R2 for dqSAD dqSRS for uniform & Logseries
#
g <- plotR2Dq_Side_Sp(DqT,256,64,"B") 
g
ggsave("R2Dq_UniLog_64_256.png", width=8,height=6,units="in",dpi=600) 


g <- plotR2Dq_Side_Sp(DqT,0,0,"Uniform")
g
ggsave("R2Dq_Unif_NumSp_Side.png", width=8,height=6,units="in",dpi=600) 


#
# plot of the Fit of the method for Dq
#

setwd("Simul")

zq <- readDq_fit(256,64,"Uniform")
plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Unif_64_256.png", width=8,height=6,units="in",dpi=600) 

## another version of the plot
#g <- plotDqFitGQ(zq,c(-10,-4,-1,0,1,4,10))


setwd("Simul")
zq <- readDq_fit(256,8,"Uniform")
plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Unif_8_256.png", width=8,height=6,units="in",dpi=600) 

setwd("Simul")
zq <- readDq_fit(256,256,"Uniform")
plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Unif_256_256.png", width=8,height=6,units="in",dpi=600) 


```


## Plots for publication Logseries SAD 

```{r plots_logser_spDq, eval=F,echo=F,message=F,warning=F}


g <- plotDq_Side_Sp(DqT,256,0,"Logseries")
g
ggsave("Dq_Logser_NumSp_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,512,0,"Logseries")
g
ggsave("Dq_Logser_NumSp_512.png", width=8,height=6,units="in",dpi=600)


#
# Plot R2 for dqSAD dqSRS
#

g <- plotR2Dq_Side_Sp(DqT,0,0,"Logseries")
g

g <- plotR2Dq_Side_Sp(DqT,0,0,"Neutral")
g

#
# plot of the Fit of the method for Dq
#

setwd("Simul")

zq <- readDq_fit(256,64,"Logseries")
plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Logser_64_256.png", width=8,height=6,units="in",dpi=600) 

setwd("Simul")

zq <- readDq_fit(256,8,"Logseries")
plotDqFitG(zq)

setwd(oldcd)
ggsave("DqFit_Logser_8_256.png", width=8,height=6,units="in",dpi=600) 

setwd("Simul")
zq <- readDq_fit(256,256,"Logseries")
plotDqFitG(zq)
setwd(oldcd)
ggsave("DqFit_Logser_256_256.png", width=8,height=6,units="in",dpi=600) 

```

## Generate Tables with R2 proportions

```{r R2tbl_Dq, eval=F,echo=F,message=F,warning=F}

#
# Generate Tables with R2 proportions
#
require(dplyr)
hh <-function(x,c,...){
  length(x[x>c])/length(x)
}

Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform",Side==256,NumSp==8,Type=="DqSAD") 

Dq1 <- filter(DqT, SAD=="Logseries" | SAD=="Uniform") %>%
  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Random","Regular")) %>%
  group_by(DqType,SAD,SpatialPattern,NumSp,Side) %>% 
  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9)) 

write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)

#
# The same for neutral simulations with logseries metacommunity 
#

Dq1 <- filter(DqT, SAD=="Neutral" | SAD=="NeuUnif") %>%
  mutate(DqType=ifelse(grepl("SRS",Type),"SRS","SAD"), SpatialPattern=ifelse(grepl("rnz",Type),"Randomized","Unmodified")) %>%
  group_by(SAD,SpatialPattern,DqType,NumSp,Side) %>% 
  summarize(Freq60=hh(R.Dq,.6),Freq90=hh(R.Dq,.9)) 


names(SadT)
Sad1 <- filter(SadT, SAD=="Neutral") %>%
  group_by(Type,Side,NumSp,SAD,rep) %>% summarize(NumSpAct=n()) %>% summarize(meanNumSp=mean(NumSpAct),rangeSp=paste(range(NumSpAct),collapse="-"))

# Merge Sad1 with Dq1 for meanNumSp
unique(Sad1$Type)
unique(Dq1$DqType)
Dq1 <- inner_join(Dq1,Sad1) %>% select(SAD, meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
pow <- distinct(select(pow_ADq24,NumSp,spMeta))

Dq1 <- left_join(Dq1,pow)  %>% 
    select(SAD, spMeta,meanNumSp,Side,SpatialPattern,DqType,Freq60,Freq90)
names(Dq1)
write.table(format(Dq1,digits=2), file = "Dq1.dat", sep = "  ", row.names = F,quote = F)


rm(Dq1,Sad1,pow)
```
