# Multifractal analysis of multispecies spatial distributions - Spatial patterns simulations



I generate different a spatial patterns to compare SRSDq SADdq and SAD

```{r setup, eval=T }

simul  <- F # variable to perform or not the simulations

oldcd <-getwd()
source("R/Neutral_fun.r")

# Set the location of the binary 
#
mfBin <- "~/Dropbox/cpp/SpatialAnalysis/mfsba" # /mfSBA /multiSpeciesSBA
pmBin <- "~/Dropbox/cpp/SpatialAnalysis/p-model/pmodel" 



require(pander)
panderOptions('table.split.table',Inf)

```

# Banded pattern 64 species 256 side

First generate a pattern with  SAR z=1 using simply bands of species z=0.5 because I am using area as Borda-de-Agua instead of side.

```{r simul_z1, eval=T,echo=F,message=F,warning=F}
setwd("Simul")


spa <- genBand_image(64,256)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_256.sed")

Dq1<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"
hist(Dq1$R)

spa <- matrix(sample(spa),nrow=256)
save_matrix_as_sed(spa,"band64_256rnz.sed")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_density(alpha=0.2)

plot_sed_image(spa,"Randomized 64sp")



Dq2<- calcDq_multiSBA("band64_256.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "dqSAD"
Dq3<- Dq2
plotDq(Dq3,"Type")

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

plotDqFit("t.band64_256rnz.sed","q.sed")

# Analizing this last it means that the scaling is broken at side 16
#  

Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 16 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")


Dq2<- calcDq_multiSBA("band64_256rnz.sed","q.sed 2 16 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD2-16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")
# copy pomExp.lin to pomac.lin
#system("cp pomExp.lin pomac.lin")

# make simulations
#if(simul) system(paste(neuBin,"sim.par","fishE.inp"),wait=s_wait)

setwd(oldcd)
```

* For SRS the positive part seems to reflect the equal SAD and the negative the spatial pattern


# Banded pattern 64 species 512 side

To see if there is any efect of side 

```{r simul_z1_512, eval=T,echo=F,message=F,warning=F}
setwd("Simul")


spa <- genBand_image(64,512)
plot_sed_image(spa,"Banded 64sp")
save_matrix_as_sed(spa,"band64_512.sed")

Dq1<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"

spa <- matrix(sample(spa),nrow=512)
save_matrix_as_sed(spa,"band64_512rnz.sed")

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)

plot_sed_image(spa,"Randomized 64sp")

Dq2<- calcDq_multiSBA("band64_512.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "dqSAD"
Dq3<- Dq2

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

plotDqFit("t.band64_512rnz.sed","q.sed")

# Analizing this last it means that the scaling is broken at side 16
#  

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 16 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD16-512"
Dq3<- rbind(Dq3,Dq2)

Dq2<- calcDq_multiSBA("band64_512rnz.sed","q.sed 2 16 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD2-16"
Dq3<- rbind(Dq3,Dq2)
plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2,binwidth = 0.1,position="identity")

setwd(oldcd)
```

Thus DqSAD works in the range 2-16 

# Now simulate an image with logseries SAD for 64 species

* Discrete bands?
* Random


```{r simul_ls_512, eval=T,echo=F,message=F,warning=F}
setwd("Simul")

require(untb)
side <- 512
N <- side*side
S <- 64 
repeat {
  ff<-fisher.ecosystem(N=N,S=S,nmax=N)
  nsp <- nrow(ff)
  if(nsp==S) break
}
plot(ff)
N
spa <- matrix(rep(1:nsp,ff),nrow=side)
plot_sed_image(spa,"Regular Fisher  64sp")
save_matrix_as_sed(spa,"fish64_512.sed")

Dq1<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 S",mfBin,T)
Dq1$Type <- "SRS"

# 
spa <- matrix(sample(spa),nrow=512)
save_matrix_as_sed(spa,"fisher64_512rnz.sed")
plot_sed_image(spa,"Rnz Fisher  64sp",0,64,5)

Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 S",mfBin,T)
Dq2$Type <- "rnzSRS"
Dq1<- rbind(Dq1,Dq2)
plotDq(Dq1,"Type")

ggplot(Dq1, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)

# Ahora con SAD

Dq3<- calcDq_multiSBA("fish64_512.sed","q.sed 4 512 20 E",mfBin,T)
Dq3$Type <- "DqSAD"
#Dq3<- rbind(Dq3,Dq2)

Dq2<- calcDq_multiSBA("fisher64_512rnz.sed","q.sed 4 512 20 E",mfBin,T)
Dq2$Type <- "rnzDqSAD"
Dq3<- rbind(Dq3,Dq2)

plotDq(Dq3,"Type")

ggplot(Dq3, aes(x=R.Dq,fill=Type)) + geom_histogram(alpha=0.2)
Dq3[Dq3$R.Dq<0.6,]
setwd(oldcd)
```